### 2025-09-25 paper/sec/evaluation.tex

@@

\begin{table}[h!]
    \scriptsize

    \centering
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 68.2   & 3.2 & 77.4 & 2 \\
            Data Retrieval & 77.3   & 3.7 & 77.4 & 2 \\
            Difference     & 20.0   & 44.7 & 77.4 & 2 \\
            Min/max        & 97.0   & 5.6 & 77.4 & 2 \\
            Rank           & 0.0   & 0.0 & 77.4 & 2 \\
            Sum            & 100   & 0.0 & 77.4 & 2 \\
            Ratio          & 100   & 0.0 & 77.4 & 2 \\
            Agerage        & 100   & 0.0 & 77.4 & 2 \\
            Overall        & 74.9 & 3 & 77.4 & 2 \\
            \hline
        \end{tabular}
        \caption{Results with target-value = true}
        \label{tab:results_true}
    \end{subtable}%
    \hfill
    \begin{subtable}{0.45\linewidth}
        \centering
        \begin{tabular}{lcccc}
            \hline
            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
            \hline
            Comparison     & 33.3 & 3.1 & -- & -- \\
            Data Retrieval & 62.0 & 1.6 & -- & -- \\
            Difference     & 75.0 & 50.0 & -- & -- \\
            Min/max        & 90.6 & 12.6 & -- & -- \\
            Rank           & 0.0 & 0.0 & -- & -- \\
            Sum            & 100.0 & 0.0 & -- & -- \\
            Ratio          & 100.0 & 0.0 & -- & -- \\
            Average        & 100.0 & 0.0 & -- & -- \\
            Overall        & 57.1 & 0.8 & -- & -- \\
            \hline
        \end{tabular}
        \caption{Results without target-value}
        \label{tab:results_no_target}
    \end{subtable}
    \caption{Success rates (with standard deviation) for \textbf{\gptfour} and \textbf{\gptfive} across different task categories}
    \label{tab:results_combined}
\end{table}

Table \ref{tab:results_combined} summarizes the performance of \gptfour and the most recent OpenAI model,
\gptfive, under two different settings: with target-value sharing enabled and without target-value sharing.
Overall, the system produced a valid Fluid expression in 74.9\% of the cases (S.D. 3\%).

Figure~\ref{fig:success_rate_by_category} illustrates the success rate for each category, both with and without target-value sharing.
The results show that providing the target value is crucial for achieving a high success rate.
Moreover, the \InterpretationAgent generates a correct expression in approximately XX\% of the cases.

>>>>

%\begin{table}[h!]
%    \scriptsize
%
%    \centering
%    \begin{subtable}{0.45\linewidth}
%        \centering
%        \begin{tabular}{lcccc}
%            \hline
%            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
%            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
%            \hline
%            Comparison     & 68.2   & 3.2 & 77.4 & 2 \\
%            Data Retrieval & 77.3   & 3.7 & 77.4 & 2 \\
%            Difference     & 20.0   & 44.7 & 77.4 & 2 \\
%            Min/max        & 97.0   & 5.6 & 77.4 & 2 \\
%            Rank           & 0.0   & 0.0 & 77.4 & 2 \\
%            Sum            & 100   & 0.0 & 77.4 & 2 \\
%            Ratio          & 100   & 0.0 & 77.4 & 2 \\
%            Agerage        & 100   & 0.0 & 77.4 & 2 \\
%            Overall        & 74.9 & 3 & 77.4 & 2 \\
%            \hline
%        \end{tabular}
%        \caption{Results with target-value = true}
%        \label{tab:results_true}
%    \end{subtable}%
%    \hfill
%    \begin{subtable}{0.45\linewidth}
%        \centering
%        \begin{tabular}{lcccc}
%            \hline
%            & \multicolumn{2}{c}{\textbf{\gptfour}} & \multicolumn{2}{c}{\textbf{\gptfive}} \\
%            & \textbf{Success Rate (\%)} & \textbf{SD (\%)} & \textbf{Success Rate} & \textbf{SD (\%)} \\
%            \hline
%            Comparison     & 33.3 & 3.1 & -- & -- \\
%            Data Retrieval & 62.0 & 1.6 & -- & -- \\
%            Difference     & 75.0 & 50.0 & -- & -- \\
%            Min/max        & 90.6 & 12.6 & -- & -- \\
%            Rank           & 0.0 & 0.0 & -- & -- \\
%            Sum            & 100.0 & 0.0 & -- & -- \\
%            Ratio          & 100.0 & 0.0 & -- & -- \\
%            Average        & 100.0 & 0.0 & -- & -- \\
%            Overall        & 57.1 & 0.8 & -- & -- \\
%            \hline
%        \end{tabular}
%        \caption{Results without target-value}
%        \label{tab:results_no_target}
%    \end{subtable}
%    \caption{Success rates (with standard deviation) for \textbf{\gptfour} and \textbf{\gptfive} across different task categories}
%    \label{tab:results_combined}
%\end{table}

@@

%Table \ref{tab:results_combined} summarizes the performance of \gptfour and the most recent OpenAI model, \gptfive, under two different settings: with target-value sharing enabled and without target-value sharing.
%Overall, the system produced a valid Fluid expression in 74.9\% of the cases (S.D. 3\%).

%Figure~\ref{fig:success_rate_by_category} illustrates the success rate of \gptfour % under two different settings: with target-value sharing enabled and without target-value sharing.
%for each category, both with and without target-value sharing.
%Overall, the system produced a valid Fluid expression in 74.9\% of the cases (S.D. 3\%) \cdnote{this needs to be updated for target sharing and not target sharing or removed}.

%Table \ref{tab:results_combined} summarizes the performance of \gptfour and the most recent OpenAI model,
%\gptfive, under two different settings: with target-value sharing enabled and without target-value sharing.
%Overall, the system produced a valid Fluid expression in 74.9\% of the cases (S.D. 3\%).

In this section, we report the experimental results.
Figure~\ref{fig:success_rate_by_category} illustrates the success rate for each category, both with and without target-value sharing.
The results show that providing the target value is crucial for achieving a high success rate.
Moreover, the \InterpretationAgent generates a correct expression in approximately XX\% of the cases.

### 2025-09-25 paper/sec/related-work.tex

\paragraph{Argument mining.}
For over fifteen years the field of NLP has been exploring the problem of argument mining, which involves
identifying argumentative structures in text, such as claims, premises, and conclusions, and mapping them to
formal representations~\citep{palau2009argumentation,lippi2015argument} . Early work in this area focused on
rule-based approaches, while more recent work has leveraged machine learning and deep learning techniques to
improve performance~\citep{stab2014identifying,stab2017parsing,eger2017neural}. The field has also emphasized
defining annotation schemes for the task, such as the Argumentative Zoning
framework~\citep{teufel2002summarizing,teufel2009towards}, as well as schemes more directly tailored to
argument mining~\citep{stab2014annotating}. The field has focused on various domains, starting from legal
texts~\citep{toulmin2003uses}, and has relied on online resources such as
Debatepedia~\citep{cabrio2013natural}. The community has also rapidly engaged with work that explores the use
of argument mining in scientific texts~\citep{liakata2012automatic,lauscher2018investigating} to better
understand the structure of scientific arguments and the relationships between different claims and evidence.
While the advent of LLMs has improved performance~\citep{gorur2025can,vrakatseli2025can}, argument mining
remains a challenging task, particularly when it comes to identifying implicit argumentative relations between
discourse units, and reasoning about relationships among different argumentative components, especially in
cross-domain settings where models struggle to generalise~\citep{gemechu2024aries}. While in our work we do
not directly perform traditional argument mining, this work similarly relies on the identification of claims
in text, which we evaluate following established practices in the field.

>>>>

\paragraph{Argument mining.}
For over fifteen years the field of NLP has been exploring the problem of argument mining, which involves
identifying argumentative structures in text, such as claims, premises, and conclusions, and mapping them to
formal representations~\citep{palau2009argumentation,lippi2015argument} . Early work in this area focused on
rule-based approaches, while more recent work has leveraged machine learning and deep learning techniques to
improve performance~\citep{stab2014identifying,stab2017parsing,eger2017neural}. The field has also emphasized
defining annotation schemes for the task, such as the Argumentative Zoning
framework~\citep{teufel2002summarizing,teufel2009towards}, as well as schemes more directly tailored to
argument mining~\citep{stab2014annotating}. The field has focused on various domains, starting from legal
texts~\citep{toulmin2003uses}, and has relied on online resources such as
Debatepedia~\citep{cabrio2013natural}. The community has also rapidly engaged with work that explores the use
of argument mining in scientific texts~\citep{liakata12,lauscher2018investigating} to better understand the
structure of scientific arguments and the relationships between different claims and evidence. While the
advent of LLMs has improved performance~\citep{gorur2025can,vrakatseli2025can}, argument mining remains a
challenging task, particularly when it comes to identifying implicit argumentative relations between discourse
units, and reasoning about relationships among different argumentative components, especially in cross-domain
settings where models struggle to generalise~\citep{gemechu2024aries}. While in our work we do not directly
perform traditional argument mining, this work similarly relies on the identification of claims in text, which
we evaluate following established practices in the field.
